---
title: "Week2_Quiz"
author: "Ilya Maltsev"
date: '1 June 2017'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

```{r, question 1 load data}
library(caret)
library(AppliedPredictiveModeling)
data(AlzheimerDisease)
```

Which of the following commands will create non-overlapping training and test sets with about 50% of the observations assigned to each?

Answer:

```{r question 1 answer}
adData = data.frame(diagnosis,predictors)
trainIndex = createDataPartition(diagnosis, p = 0.50,list=FALSE)
training = adData[trainIndex,]
testing = adData[-trainIndex,]
```

## Qustion 2

```{r, question 2 load data}
library(AppliedPredictiveModeling)
data(concrete)
library(caret)
set.seed(1000)
inTrain = createDataPartition(mixtures$CompressiveStrength, p = 3/4)[[1]]
training = mixtures[ inTrain,]
testing = mixtures[-inTrain,]
library(Hmisc)
```

Make a plot of the outcome (CompressiveStrength) versus the index of the 
samples. Color by each of the variables in the data set (you may find the 
cut2() function in the Hmisc package useful for turning continuous covariates 
into factors). What do you notice in these plots?

```{r, question 2 outcome versus index colored by Cement}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Cement, g = 3))
```

```{r, question 2 outcome versus index colored by Blast Furnace Slag}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$BlastFurnaceSlag, g = 3))
```

```{r, question 2 outcome versus index colored by Fly Ash}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$FlyAsh, g = 4))
```

```{r, question 2 outcome versus index colored by Water}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Water, g = 4))
```

```{r, question 2 outcome versus index colored by Superplasticizer}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Superplasticizer, g = 3))
```

```{r, question 2 outcome versus index colored by Coarse Aggregate}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$CoarseAggregate, g = 3))
```

```{r, question 2 outcome versus index colored by Fine Aggregate}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$FineAggregate, g = 3))
```

```{r, question 2 outcome versus index colored by Age}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Age, g = 4))
```
