---
title: "Тест. Вопрос 2"
author: "Ilya Maltsev"
date: '9 июня 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Qustion 2

```{r q2 load data}
library(AppliedPredictiveModeling)
data(concrete)
library(caret)
set.seed(1000)
inTrain = createDataPartition(mixtures$CompressiveStrength, p = 3/4)[[1]]
training = mixtures[inTrain,]
testing = mixtures[-inTrain,]
library(Hmisc)
```

Make a plot of the outcome (CompressiveStrength) versus the index of the 
samples. Color by each of the variables in the data set (you may find the 
cut2() function in the Hmisc package useful for turning continuous covariates 
into factors). What do you notice in these plots?

Possible answers:

1. There is a non-random pattern in the plot of the outcome versus index that 
does not appear to be perfectly explained by any predictor suggesting a 
variable may be missing.

2. There is a non-random pattern in the plot of the outcome versus index.

3. There is a non-random pattern in the plot of the outcome versus index that 
is perfectly explained by the Age variable.

4. There is a non-random pattern in the plot of the outcome versus index that 
is perfectly explained by the FlyAsh variable. *Yes?*

### Compressive Strength versus Index colored by variables

```{r colored by Cement}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Cement, g = 3))
```

```{r colored by Blast Furnace Slag}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$BlastFurnaceSlag, g = 3))
```

```{r colored by Fly Ash}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$FlyAsh, g = 3))
```

```{r colored by Water}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Water, g = 4))
```

```{r colored by Superplasticizer}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Superplasticizer, g = 3))
```

```{r colored by Coarse Aggregate}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$CoarseAggregate, g = 3))
```

```{r colored by Fine Aggregate}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$FineAggregate, g = 3))
```

```{r colored by Age}
plot(1:dim(training)[1], training$CompressiveStrength, 
     col = cut2(training$Age, g = 3))
```

### Compressive Strength versus Age

```{r Strength versus Age}
library(splines)
bsBasis = bs(training$Age, df = 3)
plot(training$Age, training$CompressiveStrength)
points(training$Age, 
      predict(lm(CompressiveStrength ~ bsBasis, data = training), 
              newdata = training), 
      col = "red")

plot(training$Age, training$CompressiveStrength)
# I(Age*Age) + Age
points(training$Age, 
      predict(lm(CompressiveStrength ~ I(atan(Age/25)) + I(Age*Age), data = training), 
              newdata = training), 
      col = "red")
summary(lm(CompressiveStrength ~ I(atan(Age/25)) + I(Age*Age) + Cement + Water + BlastFurnaceSlag + Superplasticizer, data = training))
```

### Model

```{r q2 model}
# training2 = training
# training2$fBlastFurnaceSlag = cut2(training$BlastFurnaceSlag, g = 3)
# training2$fSuperplasticizer = cut2(training$Superplasticizer, g = 3)
# training2$bsBasis1 = bsBasis[,1]
# training2$bsBasis2 = bsBasis[,2]
# training2$bsBasis3 = bsBasis[,3]
# lm5 = lm(CompressiveStrength ~ Age + Cement + Water + 
#             fBlastFurnaceSlag + fSuperplasticizer, 
#         data = training2)
# summary(lm5)

lm5 = train(CompressiveStrength ~ Cement + Age + Water + 
                BlastFurnaceSlag + Superplasticizer, method = "lm", data = training)
pred = predict(lm5, testing)
qplot(CompressiveStrength, pred, data = testing)
```
