---
title: "Тест. Вопрос 3"
author: "Ilya Maltsev"
date: '9 июня 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 3

Make a histogram and confirm the SuperPlasticizer variable is skewed. 
Normally you might use the log transform to try to make the data more 
symmetric. Why would that be a poor choice for this variable?

Possible answers:

1. The log transform produces negative values which can not be used by some classifiers.

2. The SuperPlasticizer data include negative values so the log transform 
can not be performed.

3. There are values of zero so when you take the log() transform those values 
will be -Inf. *Yes?*

4. The log transform does not reduce the skewness of the non-zero values 
of SuperPlasticizer.

```{r q3 load data}
library(AppliedPredictiveModeling)
data(concrete)
library(caret)
set.seed(1000)
inTrain = createDataPartition(mixtures$CompressiveStrength, p = 3/4)[[1]]
training = mixtures[ inTrain,]
testing = mixtures[-inTrain,]
```

```{r q3 hist}
hist(testing$Superplasticizer, breaks = 20)
```
