---
title: "Тест. Вопрос 5"
author: "Ilya Maltsev"
date: '9 июня 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Вопрос 5

Load the Alzheimer's disease data using the commands:
    
```{r load data}
library(caret)
library(AppliedPredictiveModeling)
set.seed(3433)
data(AlzheimerDisease)
adData = data.frame(diagnosis,predictors)
inTrain = createDataPartition(adData$diagnosis, p = 3/4)[[1]]
training = adData[ inTrain,]
testing = adData[-inTrain,]
```

Create a training data set consisting of only the predictors with variable 
names beginning with IL and the diagnosis. Build two predictive models, one 
using the predictors as they are and one using PCA with principal components 
explaining 80% of the variance in the predictors. Use method="glm" in the 
train function.

What is the accuracy of each method in the test set? Which is more accurate?

1. Non-PCA Accuracy: 0.75
PCA Accuracy: 0.71

2. Non-PCA Accuracy: 0.72
PCA Accuracy: 0.71

3. Non-PCA Accuracy: 0.72
PCA Accuracy: 0.65

4. Non-PCA Accuracy: 0.65
PCA Accuracy: 0.72

```{r selecting IL predictors}
ILnames <- names(training)[startsWith(names(training), "IL")]
ILtraining <- training[, c("diagnosis", ILnames)]
ILtesting <- testing[, c("diagnosis", ILnames)]
```

```{r train with all IL predictors}
fit.all <- train(diagnosis ~ ., method = "glm", data = ILtraining)
fit.all.prediction <- predict(fit.all, ILtesting[, -c(1)])
fit.all.confusionMatrix <- confusionMatrix(ILtesting$diagnosis, fit.all.prediction)
print(fit.all.confusionMatrix)
fit.all.accuracy <- fit.all.confusionMatrix$overall["Accuracy"]
```

```{r pca analysis}
prcomp.res <- prcomp(ILtraining[, -c(1)], scale. = TRUE)
s <- summary(prcomp.res)
cumulativeProportion <- s$importance[3,]
latestImportantComponent <- which.min(cumulativeProportion <= 0.8)
```

```{r train with pca}
preProc <- preProcess(ILtraining[, -c(1)], method = "pca", 
                      pcaComp = latestImportantComponent)
trainPCA <- predict(preProc, ILtraining[, -c(1)])
trainPCA$diagnosis <- ILtraining$diagnosis
fit.pca <- train(diagnosis ~ ., method = "glm", data = trainPCA)
testPCA <- predict(preProc, ILtesting[, -c(1)])
fit.pca.prediction <- predict(fit.pca, testPCA)
fit.pca.confusionMatrix <- confusionMatrix(ILtesting$diagnosis, fit.pca.prediction)
print(fit.pca.confusionMatrix)
fit.pca.accuracy <- fit.pca.confusionMatrix$overall["Accuracy"]
```

```{r answer}
print(paste("NON-PCA", round(fit.all.accuracy, 2)))
print(paste("PCA", round(fit.pca.accuracy, 2)))
```
Ответ: NON-PCA - 0.65, PCA - 0.72
