---
title: "Тест. Вопрос 1"
author: "Илья Мальцев"
date: '25 декабря 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
```

Load the vowel.train and vowel.test data sets:

```{r load data}
library(ElemStatLearn)
data(vowel.train)
data(vowel.test)
```

Set the variable y to be a factor variable in both the training and test set. Then set the seed to 33833. Fit (1) a random forest predictor relating the factor variable y to the remaining variables and (2) a boosted predictor using the "gbm" method. Fit these both with the train() command in the caret package.

What are the accuracies for the two approaches on the test data set? What is the accuracy among the test set samples where the two methods agree?

    1. RF Accuracy = 0.9881
    GBM Accuracy = 0.8371
    Agreement Accuracy = 0.9983

    2. RF Accuracy = 0.6082
    GBM Accuracy = 0.5152
    Agreement Accuracy = 0.5152

    3. RF Accuracy = 0.9987
    GBM Accuracy = 0.5152
    Agreement Accuracy = 0.9985
    
    4. RF Accuracy = 0.6082
    GBM Accuracy = 0.5152
    Agreement Accuracy = 0.6361


```{r prepare}
w.vowel.train = as.data.frame(vowel.train)
w.vowel.train$y = as.factor(w.vowel.train$y)
w.vowel.test = as.data.frame(vowel.test)
w.vowel.test$y = as.factor(w.vowel.test$y)
```

```{r set seed}
set.seed(33833)
```

```{r setup cluster}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1)
registerDoParallel(cluster)
```

```{r rf}
library(caret)
rfFit = train(y ~ ., w.vowel.train, method = "rf")
```

```{r boost}
boostFit = train(y ~ ., w.vowel.train, method = "gbm")
```

```{r destroy cluster}
stopCluster(cluster)
registerDoSEQ()
```

```{r accuracies}
rfPred = predict(rfFit, newdata = w.vowel.test)
rfAccurary = sum(rfPred == w.vowel.test$y) / length(w.vowel.test$y)
boostPred = predict(boostFit, newdata = w.vowel.test)
boostAccurary = sum(boostPred == w.vowel.test$y) / length(w.vowel.test$y)
agreementIndex = rfPred==boostPred
agreementAccuracy = sum(w.vowel.test$y[agreementIndex] == rfPred[agreementIndex]) / length(agreementIndex[agreementIndex])
print(paste("RF accurary: ", round(rfAccurary, 2)))
print(paste("GBM accurary: ", round(boostAccurary, 2)))
print(paste("Agreement accurary: ", round(agreementAccuracy, 2)))
```

Ответ: 4

Точные значения не совпадают
