---
title: "Тест. Вопрос 4"
author: "Илья Мальцев"
date: '23 декабря 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Вопрос

Load the South Africa Heart Disease Data and create training and test sets with the following code:

```{r prepare data}
library(ElemStatLearn)
data(SAheart)
set.seed(8484)
train = sample(1:dim(SAheart)[1],size=dim(SAheart)[1]/2,replace=F)
trainSA = SAheart[train,]
testSA = SAheart[-train,]
```

Then set the seed to 13234 and fit a logistic regression model (method="glm", be sure to specify family="binomial") with Coronary Heart Disease (chd) as the outcome and age at onset, current alcohol consumption, obesity levels, cumulative tabacco, type-A behavior, and low density lipoprotein cholesterol as predictors. Calculate the misclassification rate for your model using this function and a prediction on the "response" scale:

```{r misclassification function}
missClass = function(values,prediction) {
    sum(((prediction > 0.5)*1) != values)/length(values)
}
```

What is the misclassification rate on the training set? What is the misclassification rate on the test set?

    1. Test Set Misclassification: 0.35
    Training Set: 0.31

    2. Test Set Misclassification: 0.27
    Training Set: 0.31

    3. Test Set Misclassification: 0.31
    Training Set: 0.27

    4. Test Set Misclassification: 0.43
    Training Set: 0.31
    
## Решение

```{r seed}
set.seed(13234)
```

```{r model fit}
library(caret)
modelFit = train(chd ~ age + alcohol + obesity + tobacco + typea + ldl, 
                 data = trainSA, 
                 method = "glm", family = "binomial")
```

```{r prediction}
predictionTest = predict(modelFit, testSA)
predictionTrain = predict(modelFit, trainSA)
```

```{r misclassification results}
testMiss = missClass(testSA$chd, predictionTest)
trainMiss = missClass(trainSA$chd, predictionTrain)
print(testMiss)
print(trainMiss)
```

Ответ: 3
