---
title: "Тест. Вопрос 5"
author: "Илья Мальцев"
date: '23 декабря 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Вопрос

Load the vowel.train and vowel.test data sets:

```{r load data}
library(ElemStatLearn)
data(vowel.train)
data(vowel.test)
```

Set the variable y to be a factor variable in both the training and test set. Then set the seed to 33833. Fit a random forest predictor relating the factor variable y to the remaining variables. Read about variable importance in random forests here: http://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm#ooberr The caret package uses by default the Gini importance.

Calculate the variable importance using the varImp function in the caret package. What is the order of variable importance?

[NOTE: Use randomForest() specifically, not caret, as there's been some issues reported with that approach. 11/6/2016]

    The order of the variables is:
    x.10, x.7, x.9, x.5, x.8, x.4, x.6, x.3, x.1,x.2

    The order of the variables is:
    x.2, x.1, x.5, x.6, x.8, x.4, x.9, x.3, x.7,x.10
    
    The order of the variables is:
    x.1, x.2, x.3, x.8, x.6, x.4, x.5, x.9, x.7,x.10

    The order of the variables is:
    x.10, x.7, x.5, x.6, x.8, x.4, x.9, x.3, x.1,x.2

## Решение

```{r set seed}
set.seed(33833)
```

```{r prepare data}
vowel.test$y = factor(vowel.test$y)
vowel.train$y = factor(vowel.train$y)
```

```{r fit a model}
library(randomForest)
modelFit = randomForest(y ~ ., vowel.train)
```

```{r calculate importance}
library(caret)
library(dplyr)
varImp(modelFit)
imp[order(imp, decreasing = T), , drop = FALSE]
```

Ответ: 2
