---
title: "Тест. Вопрос 3"
author: "Илья Мальцев"
date: '23 декабря 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Вопрос

Load the olive oil data using the commands:
```{r, load data}
library(pgmm)
data(olive)
olive = olive[,-1]
```

These data contain information on 572 different Italian olive oils from multiple regions in Italy. Fit a classification tree where Area is the outcome variable. Then predict the value of area for the following data frame using the tree command with all defaults

```{r}
newdata = as.data.frame(t(colMeans(olive)))
```

What is the resulting prediction? Is the resulting prediction strange? Why or why not?

    1. 2.783. It is strange because Area should be a qualitative variable - but tree is reporting the average value of Area as a numeric variable in the leaf predicted for newdata
    
    2. 4.59965. There is no reason why the result is strange.
    
    3. 0.005291005 0 0.994709 0 0 0 0 0 0. The result is strange because Area is a numeric variable and we should get the average within each leaf.
    
    4. 2.783. There is no reason why this result is strange.

## Ответ

```{r fit}
library(caret, quietly = TRUE)
modelFit = train(Area ~ ., olive, method = "rpart")
```

```{r plot fit}
plot(modelFit$finalModel)
text(modelFit$finalModel)
```

```{r predict}
predict(modelFit, newdata = newdata)
```

Ответ - 1.
