---
title: "Тест. Вопрос 1"
author: "Илья Мальцев"
date: '17 июня 2017 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Вопрос

For this quiz we will be using several R packages. R package versions change 
over time, the right answers have been checked using the following versions 
of the packages.

    AppliedPredictiveModeling: v1.1.6
    caret: v6.0.47
    ElemStatLearn: v2012.04-0
    pgmm: v1.1
    rpart: v4.1.8

If you aren't using these versions of the packages, your answers may not 
exactly match the right answer, but hopefully should be close.

Load the cell segmentation data from the AppliedPredictiveModeling package 
using the commands:

```{r, load data}
library(AppliedPredictiveModeling, quietly = TRUE)
data(segmentationOriginal)
library(caret, quietly = TRUE)
```

    1. Subset the data to a training set and testing set based on the Case 
    variable in the data set.
    2. Set the seed to 125 and fit a CART model with the rpart method using all 
    predictor variables and default caret settings.
    3. In the final model what would be the final model prediction for cases with 
    the following variable values:
        a. TotalIntenCh2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1=2
        b. TotalIntenCh2 = 50,000; FiberWidthCh1 = 10; VarIntenCh4 = 100
        c. TotalIntenCh2 = 57,000; FiberWidthCh1 = 8; VarIntenCh4 = 100
        d. FiberWidthCh1 = 8; VarIntenCh4 = 100; PerimStatusCh1=2

    1.
        a. PS
        b. Not possible to predict
        c. PS
        d. Not possible to predict
    2. 
        a. Not possible to predict
        b. WS
        c. PS
        d. PS
    3. 
        a. PS
        b. WS
        c. PS
        d. WS
    4. *
        a. PS
        b. WS
        c. PS
        d. Not possible to predict

## Решение

```{r subset training and testing sets}
trainingSet <- segmentationOriginal[which(segmentationOriginal$Case == 'Train'),]
testingSet <- segmentationOriginal[which(segmentationOriginal$Case == 'Test'),]
```

```{r settings}
set.seed(125)
```

```{r fit model}
fit <- train(Class ~ ., trainingSet, method = "rpart")
```

```{r plot fit}
plot(fit$finalModel)
text(fit$finalModel)
```

```{r predict}
newdataA <- trainingSet[1,]
newdataA[,"TotalIntenCh2"] = 23000
newdataA[,"FiberWidthCh1"] = 10
newdataA[,"PerimStatusCh1"] = 2
predictionA <- predict(fit, newdata = newdataA)

newdataB <- trainingSet[1,]
newdataB[,"TotalIntenCh2"] = 50000
newdataB[,"FiberWidthCh1"] = 10
newdataB[,"VarIntenCh4"] = 100
predictionB <- predict(fit, newdata = newdataB)

newdataC <- trainingSet[1,]
newdataC[,"TotalIntenCh2"] = 57000
newdataC[,"FiberWidthCh1"] = 8
newdataC[,"VarIntenCh4"] = 2
predictionC <- predict(fit, newdata = newdataC)

newdataD <- trainingSet[1,]
newdataD[,"FiberWidthCh1"] = 8
newdataD[,"VarIntenCh4"] = 100
newdataD[,"PerimStatusCh1"] = 2
predictionD <- predict(fit, newdata = newdataD)

print(paste(predictionA, predictionB, predictionC, predictionD))
```

